TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-09-21 paper/draft.tex
typo
update

We note that surface gravity is not inclided as a training label. The reason for this is that for main-sequence M dwarfs, the parameter is almost entirely redundant with metallicity. Unlike their higher-mass counterparts, M dwarf properties do not change measurably over the age of the Universe. Hence perfect knowledge of abundances and \teff\ for an M dwarf should uniquely determine its position its surface gravity, position on a color-magnitude diagram, and overall luminosity. While we only had [Fe/H] for the training sample, for the uncertainties considered here, lack of information about [$\alpha$/Fe] or specific abundances will only be important for extreme cases (e.g., Carbon stars).

@@

In \citealt{Schmidt:2016} the authors used three different color-temperature relations to check the consistency of \aspcap\ temperature values using a combination of \zmass\ and visual band photometries. \color{gcolor}{Brief description of the color-teff relations from \citealt{Casagrande:2008}, \citealt{Boyajian:2013}, and \citealt{Mann:2015}...}\color{black}.

To obtain visual band magnitudes for a set of sources, we cross-matched the 10,311 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,000 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. In Figure \ref{fig:aspcap_cannon_validation} we repeat the temperature validation tests for each of the three relations and compare the \aspcap\ temperatures for the same sources. \color{gcolor}{Comments about validation results and the uncertainty of our Cannon temperatures...}\color{black}

\color{gcolor}{What are all of the parameters we want to report and what do we want to emphasize? Are there other parameters (such as mass) that might be straightforward to estimate?}\color{black}

>>>>

We note that surface gravity is not included as a training label. The reason for this is that for main-sequence M dwarfs, the parameter is almost entirely redundant with metallicity. Unlike their higher-mass counterparts, M dwarf properties do not change measurably over the age of the Universe. Hence perfect knowledge of abundances and \teff\ for an M dwarf should uniquely determine its position its surface gravity, position on a color-magnitude diagram, and overall luminosity. While we only had [Fe/H] for the training sample, for the uncertainties considered here, lack of information about [$\alpha$/Fe] or specific abundances will only be important for extreme cases (e.g., Carbon stars).

@@

As a validation test of our derived temperatures, we perform a comparison between several color-temperature relations, which use combination of \zmass\ and visual band photometries to predict temperatures. SUMMARIZE \citealt{Casagrande:2008}, \citealt{Boyajian:2013}, and \citealt{Mann:2015}

To obtain visual band magnitudes for a set of sources, we cross-matched the 10,311 sources in our ``safe'' test sample to the AAVSO Photometric All-Sky Survey DR9 (APASS; \citealt{Henden:2016}), to obtain a subsample of 6,000 sources with both $BV$ photometries measured by APASS, and $JHK$ photometries from \apogee. Figure \ref{fig:aspcap_cannon_validation} shows the temperature validation tests for each of the three relations and compared to the \aspcap\ temperatures for the same sources. \color{gcolor}{Comments about validation results and the uncertainty of our Cannon temperatures...}\color{black}
